Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-13 paper/disc20clustering.tex
defining component

%\medskip
%In our algorithms, 
A~\emph{component} is a~subset of frequently communicating nodes \maciek{this is not a~good definition. intuitions, maybe}.
We keep all nodes of a~component always collocated in the same cluster,
i.e., when we  move a~node,
we move the whole component that contains it.
A~partition that maintains this invariant is a~\emph{component respecting} partition.
%We say that a~partition is \emph{component respecting}
%if the nodes belonging to the same component are always collocated.
We say that a~component is \emph{singleton} if it contains exactly one node,
and the node in this component is \emph{isolated}.

>>>>

We maintain subsets of frequently communicating nodes as \emph{components}.
Components 
Initially,
each node constitutes a single-node component which we refer to as a \emph{singleton} components, 
and the contained node is an \emph{isolated} node.
We define larger components in terms of smaller components.
Concretely,
given a (sub)sequence of requests,
two components $C_1$ and $C_2$
 \emph{merge} into one component as soon as
 for some pair of nodes $v_1 \in C_1$ and $v_2 \in C_2$,
the frequency of requests $\{v_1,v_2\}$ reaches a certain threshold through the sequence.
We keep all nodes of a~component always collocated in the same cluster,
i.e., when we  move a~node,
we move the whole component that contains it.
A~partition that maintains this invariant is a~\emph{component respecting} partition.
%Intuitively, a component preserves the history of requests between its nodes.
